dispRity simulate data

### 2017-08-10 doc/dispRity-simulate_data.Rmd
Updated with details from manual

@@

Quick go through
=================================
This is a quick example on how it works

@@

## Generating a matrix with 100 characters (85% binary and 15% three states) and
## an equal rates model with a gamma rates distribution (0.5, 1) with no 
## invariant characters.
my_matrix <- sim.morpho(tree = my_tree, characters = 100, states = c(0.85,
    0.15), rates = c(rgamma, 0.5, 1), invariant = FALSE)

@@

In details
=================================
Basically, `sim.morpho` is really flexible and intakes a lot of different arguments to allow to simulate realistic matrix.
It has two implemented models: `"ER"` for Equal Rates (M*k* model) or the `"HKY"` one which is the molecular HKY model but transforms pyrines in 0's and purimidines in 1's.
It can also intake some specific distribution for the rates or the substitutions, allowing to modify these basic models.

The `check.morpho` runs a quick MP tree using the `phangorn` parsimony algorithm.
It quickly calculates the parsimony score, the consistency and retention indices and, if a tree is provided (e.g. the tree used to generate the matrix) it calculates the Robinson-Foulds distance between the MP tree and the provided tree.

Good parameters for a good matrix
-----------------------------------

I was testing the effect of different parameters on the ability to generate a ``realistic'' matrix (meaning not to different from the input tree with a consistency and retention index close to what's in the literature).
The matrix seems the most ``realistic'' with a starting coalescent tree, equal rates model with 0.85 binary characters and 0.15 three states characters, a gamma distribution with a shape parameter ($\alpha$) of 0.5 and no scaling ($\beta$ = 1).

Something like that should give a decent matrix:

@@

>>>>

The `dispRity` package allows users to simulate discrete morphological data matrices.
In brief, the function `sim.morpho` takes a phylogenetic tree, the number of required characters, the evolutionary model, and a function from which to draw the rates.
The package also contains a function for quickly checking the matrix's phylogenetic signal (as defined in systematics not phylogenetic comparative methods) using parsimony.

@@

A simple example
=================================

@@

## Generating a matrix with 100 characters (85% binary and 15% three state) and
## an equal rates model with a gamma rate distribution (0.5, 1) with no 
## invariant characters.
my_matrix <- sim.morpho(tree = my_tree, characters = 100, states = c(0.85,
    0.15), rates = c(rgamma, 0.5, 1), invariant = FALSE)

@@

A more detailed description
=================================
`sim.morpho` is really flexible and takes many different arguments to allow users to simulate realistic matrices.
It has three implemented models: `"ER"` for Equal Rates (the M*k* model); `"HKY"`, the molecular HKY model but transforms pyrines in 0's and pyrimidines in 1's; or the `"mixed"` model that randomly uses an `"ER"` and/or `"HKY"` for the binary characters and `"ER"` for the multistate (>2) characters.
Both models take specific distributions for their rate or substitution models.
These distributions should be passed to these arguments in the format of `c(sampler_function, distribution_parameters)` where the the sampler function is a the random generation function of that distribution (e.g. `rnorm`, `runif`, etc...) and the parameters are any parameters to be passed to this function.

`check.morpho` runs a quick Maximum Parsimony tree search using the `phangorn` parsimony algorithm.
It quickly calculates the parsimony score, the consistency and retention indices and, if a tree is provided (e.g. the tree used to generate the matrix) it calculates the Robinson-Foulds distance between the most parsimonious tree and the provided tree to determine how different they are.

Parameters for a realistic(ish) matrix
===========================================
There are many parameters that can create a ``realistic'' matrix (i.e. not too different from the input tree with a consistency and retention index close to what is seen in the literature) but because of the randomness of the matrix generation not all end up creating "good" matrices.
The following parameters however, seem to generate fairly ``realistic'' matrices with a starting coalescent tree, equal rates model with 0.85 binary characters and 0.15 three state characters, a gamma distribution with a shape parameter ($\alpha$) of 5 and no scaling ($\beta$ = 1) with a rate of 100.
<!-- NC: Check that I haven't changed what you mean here where i swapped good for realistic. Realistic is a better term. Or be clearer what you mena by "good" -->

@@

`space.maker`
=================================
Another way to simulate data is to directly simulate an ordinated space with the `space.maker` function.
This function allows users to simulate multidimensional spaces with a certain number of properties.
It takes as arguments the number of elements (data points) and dimensions to create the space but also permits more fine tuning in the data simulation: it is possible to give a specific distribution to each dimension, provide a correlation matrix to link the dimensions or even provide an *a priori* distribution of the variance for each distributions!
<!-- added this in from the manual -->

```{r, fig.width=8, fig.height=8, eval=TRUE}
## Graphical options
op <- par(mfrow = (c(2, 2)), bty = "n")
## Visualising 3D spaces
require(scatterplot3d)

## A cube space
scatterplot3d(space.maker(2500, 3, runif), pch = 20,
              xlab = "", ylab = "", zlab = "",
              main = "Uniform cube space")

## A plane space
scatterplot3d(space.maker(2500, 3, c(runif, runif, runif),
              arguments = list(list(min = 0, max = 0), NULL, NULL)), pch = 20,
              xlab = "", ylab = "", zlab = "",
              main = "Uniform plane space")

## An ellipsoid space (=a spheric space with correlation)
cor_matrix <- matrix(cbind(1, 0.8, 0.2, 0.8, 1, 0.7, 0.2, 0.7, 1), nrow = 3)
scatterplot3d(space.maker(2500, 3, rnorm, cor.matrix = cor_matrix), pch = 20,
              xlab = "", ylab = "", zlab = "",
              main = "Normal ellipsoid space")

## A cylindrical space with a decreasing variance per axis
scatterplot3d(space.maker(2500, 3, c(rnorm, rnorm, runif),
              scree = c(0.7, 0.2, 0.1)), pch = 20,
              xlab = "", ylab = "", zlab = "",
              main = "Normal cylindrical space")

## Resetting the graphic parameters
par(op)
```
